---
title: "Beer Awards Analysis"
author: "Adriana Picoral"
date: "November 10, 2020"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

# Text Formatting

## Examples of Text Formatting

You can format words in *italics* or **bold**. 

- first item of a list
- second item of a list

1. first item in numbered list
1. second item in numbered list
1. third item in numbered list

> This is quote

# Beer Awards Analysis

Here's what my data like (displaying first six rows).

```{r message=FALSE, echo=FALSE}
# load library
library(tidyverse)

# read data in
beer_awards <- read_csv("data/clean_beer_awards.csv")

# print head
head(beer_awards) %>%
  knitr::kable()
```

My data questions are as follows:

1. Which region in the US has received the most beer awards?
1. Which beer type has won the most awards across different regions in the US?
1. Which beet type has won the most awards across different years?

## Awards per Region

First, we need to count how many beer awards per region.

```{r}
# start with beer awards data, filter out DC
# count awards (rows) per region
beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(region) %>%
  arrange(-n) %>%
  kable(col.names = c("Region in the US", "Total Number of Awards"),
        caption = "Total number of awards per region (1987-2020)")
```

We might need to consider the different number of states per regions.

```{r message=FALSE}
# start with beer awards data, filter out DC
# count awards per state and region
beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(state, region) %>%
  group_by(region) %>%
  summarise(average_awards = mean(n)) %>%
  arrange(-average_awards) %>%
  kable(col.names = c("Region in the US", "Average Number of Awards"),
        digits = 2)

```

Going back to our data question (_Which region in the US has received the most beer awards?_), I would say that it is the West.

## Analysis of Beer Types

Here's a dictionary of beer types. Macro categories (also referred to as beer type) was defined by the words used in the variable category. See Table 1 for a reference of what categories are included into each beer type.

| Macro-Category | Explanation |
| -------------- | ----------- |
| Aged | Aged beers such as Fruited Wood- and Barrel-Aged Sour Beer |
| Ale  | Ales such as American-Style Cream Ale |


```{r echo=FALSE, fig.dim=c(7, 5)}
library(tidytext)

beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(macro_category, region) %>%
  ggplot(aes(x = n,
             y = reorder_within(macro_category, n, region),
             fill = region)) +
  geom_col() +
  geom_label(aes(label = n), size = 1) +
  facet_wrap(~region, scales = "free_y") +
  scale_y_reordered() +
  labs(x = "Total Number of Awards",
       y = "",
       caption = "Data from the Great American Beer Festival") +
  theme_bw() +
  theme(legend.position = "none")
```

```{r}
# get 5 types with the most awards
beer_awards %>%
  filter(macro_category != "other") %>%
  count(macro_category) %>%
  arrange(-n)

# count macro_category and year
# draw line plot with x mapped to year, y to n, color to macro_category
beer_awards %>%
  filter(macro_category %in% c("lager", "stout", "flavored", "pilsener", "porter")) %>%
  count(macro_category, year) %>%
  ggplot(aes(x = year,
             y = n,
             color = macro_category)) +
  geom_line(aes(linetype = macro_category))
```




