---
title: "Beer Awards Analysis"
author: "Adriana Picoral"
date: "November 10, 2020"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

# Text Formatting

## Examples of Text Formatting

You can format words in *italics* or **bold**. 

- first item of a list
- second item of a list

1. first item in numbered list
1. second item in numbered list
1. third item in numbered list

> This is quote

# Beer Awards Analysis

Here's what my data like (displaying first six rows).

```{r message=FALSE, echo=FALSE}
# load library
library(tidyverse)

# read data in
beer_awards <- read_csv("data/clean_beer_awards.csv")

# print head
head(beer_awards) %>%
  knitr::kable()
```

My data questions are as follows:

1. Which region in the US has received the most beer awards?
1. Which beer type has won the awards across different regions in the US?

## Awards per Region

First, we need to count how many beer awards per region.

```{r}
# start with beer awards data, filter out DC
# count awards (rows) per region
beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(region) %>%
  arrange(-n) %>%
  kable(col.names = c("Region in the US", "Total Number of Awards"),
        caption = "Total number of awards per region (1987-2020)")
```

We might need to consider the different number of states per regions.

```{r message=FALSE}
# start with beer awards data, filter out DC
# count awards per state and region
beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(state, region) %>%
  group_by(region) %>%
  summarise(average_awards = mean(n)) %>%
  arrange(-average_awards) %>%
  kable(col.names = c("Region in the US", "Average Number of Awards"),
        digits = 2)

```

Going back to our data question (_Which region in the US has received the most beer awards?_), I would say that it is the West.

## Analysis of Beer Types

```{r}
beer_awards %>%
  count(region, macro_category) %>%
  ggplot(aes(x = n,
             y = macro_category,
             fill = region)) +
  geom_col()
```
