---
title: "Women Entrepreneurship by Country"
author: "Adriana Picoral"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
# load libraries
library(janitor)
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# read data in
women_entrepreneur_data <- read_delim("data/women_in_labor_force.csv",
                                      delim = ";") %>%
  clean_names()
```

# Introduction

In this paper, I will discuss the effect of having women entrepreneurs on a country's economy. 

# Methods

My research question is as follows:

1. What is the relationship of having more entrepreneurs in a country (no matter the gender) and that country's economy?
1. What is the relationship of having more women entrepreneurs in a country and that country's economy?
1. Do women entrepreneurs have a greater impact in the economy than just entrepreneurs in general?

## Data

The data I am using was obtained from [Kaggle](https://www.kaggle.com/babyoda/women-entrepreneurship-and-labor-force) and contains the following variables: `r colnames(women_entrepreneur_data)`. The data was collected in 2015 for `r nrow(women_entrepreneur_data)` countries.

# Analysis

The two variables we have available on economic development for each country: a binary variable called *level_of_development* (i.e., Developed vs. Developing) and *inflation_rate*. The first step in the analysis is to establish whether inflation rate is lower or higher for developed countries, assuming that developed countries have better economies. 

The box plot below shows that *developed* countries have a lower inflation rate than *developing* countries. Thus, we will assume that the lower the inflation rate, the stronger the country's economy. 

```{r}
# draw bloxplot of level_of_development by inflation_rate
women_entrepreneur_data %>%
  ggplot(aes(x = level_of_development,
             y = inflation_rate)) +
  geom_boxplot() +
  theme_linedraw() +
  labs(x = "Level of Development",
       y = "Inflation Rate",
       title = "Inflation by Development across differente countries")

```

To answer my first research question (i.e., *What is the relationship of having more entrepreneurs in a country (no matter the gender) and that country's economy?*), we need to establish the relationship between inflation and entrepreneurship index. 


```{r}
# draw scatter plot of inflation_rate vs. entrepreneurship index
women_entrepreneur_data %>%
  ggplot(aes(x = entrepreneurship_index,
             y = inflation_rate)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x)

```


